Structural Divergence Analysis

### 2017-06-04 MY-FILES/OTHER FILES/analysis-structure-antes.Rmd
estructura-CN/WCN

# load functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
source("FUNCTIONS/readCA.R") 
```

@@

@@

plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental ")
plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
```

>>>>

ReadCA.fname <- "FUNCTIONS/ReadCA.R"
CalculateSideChainCM.fname <- "FUNCTIONS/CalculateSideChainCM.R"

# load functions
source(ReadCA.fname) 
source(CalculateSideChainCM.fname)
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
source("FUNCTIONS/readCA.R") 
```

@@

if (data.dir == "OUT/out_subset_CM_ANM") {

  # Read PDB of p.ref
  pdb.ca = ReadCA(reference.pdb.fname, chain.p.ref)
  r.ca.p.ref = pdb.ca$xyz.calpha
  n.aa = pdb.ca$n.sites

  r.CM.p.ref = CalculateSideChainCM(reference.pdb.fname, chain.p.ref)
  n.CM = ncol(r.CM.p.ref)

  cmap.CM = cmap(r.CM.p.ref, dcut = R0, scut = 0, mask.lower = F)
  CN = rowSums(cmap.CM, na.rm = T) - 2
}

@@

plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")

@@

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

# mean profiles

CN.simple = CN[!duplicated(CN)]

CN.i.mean = c()
exp.mean.z.RSD.i.mean = c()
mut.mean.z.RSD.i.mean = c()
medium.mean.z.RSD.i.mean = c()

count = 0
for (i in (CN.simple)) {
  count = count + 1
  index = 0
  for (j in (1:length(CN))){
    if (CN[j] == i) {
      index = cbind(index, j)
    } 
  }
  CN.i.mean[count] = mean(CN[index])
  exp.mean.z.RSD.i.mean[count] = mean(d.exp$mean.z.RSD[index])
  mut.mean.z.RSD.i.mean[count] = mean(d.mut$mean.z.RSD[index])
  medium.mean.z.RSD.i.mean[count] = mean(d.medium$mean.z.RSD[index])
}

## plot
par(pty = "s")

plot(x = exp.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> experimental for each CN", ylab = "log(CN)")
plot(x = mut.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> no-selection for each CN", ylab = "log(CN)")
plot(x = medium.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> selection for each CN", ylab = "log(CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
```

### Sequence - structure comparison WCN

```{r structure-WCN-comparison}

plot(x = d.exp$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
